Make any stupid plot you want

### 2020-11-23 draft/sections/math.tex
mess of marks

\subsection{Data Space}
\begin{figure}[ht]
    \includegraphics[width=0.5\linewidth]{figures/sections/math/mobius.png}
    \caption{write up some words here}
    \label{fig:mobius}
\end{figure}

@@

\begin{equation*}
\rho(\Gamma(S)) = \int_{\alpha_1}^{\alpha_2}\int_{\beta_1}^{\beta_2}\int_{z_1}^{z_2}{R, G, B, A}  
\end{equation*}

@@

\begin{tikzcd}
    \xi E \arrow[rr, "\tau" description] \arrow[rd, "\xi \sigma" description, bend right] &     & H \arrow[ld] \\
    & S \arrow[lu, bend right] &             
    \end{tikzcd}

\subsubsection{Marks}

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
Visual Idioms

>>>>

\subsection{Data Space}
\begin{figure}[ht]
    \includegraphics[width=0.5\linewidth]{figures/sections/math/mobius.png}
    \caption{write up some words here}
    \label{fig:mobius}
    %%possibly replace w/ simpler deconstructed band image notes-11-19-20
\end{figure}

@@

\begin{equation*}
\rho(S) = \int_{\alpha_1}^{\alpha_2}\int_{\beta_1}^{\beta_2}\int_{z_1}^{z_2}{R, G, B, A}  
\end{equation*}

@@

\begin{tikzcd}
    \xi E \arrow[rr, "\Tau" description] \arrow[rd, "\xi \sigma" description, bend right] &     & H \arrow[ld] \\
    & S \arrow[lu, bend right] &             
    \end{tikzcd}

\subsubsection{Marks}
%% diagram of connected components/line thing
Bertin defines the physical symbols that on screen represent the data as marks 
\cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology}. For each point on the screen $s$, the mark it belongs to is

%%
The others fit perfectly. So it sounds like for each point s on the screen we can define the "mark it belongs" by mapping it back to K via lookup to S to get s, then \xi(s) back to K, and then take the connected component $J \subset containing k\in J \sub K $ and then taking the inverse image of $J \in S, \xi^(-1)(J)$ and then map into $R^7  \rho(\xi^(-1)(J))$ and project into the x-y plane. So thats the mark and the thing the mark "signifies" is J.

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
Two artists are equivalent when given data containers $\Gamma(E)$ of the same type, they output the same type of prerender $\Gamma(S)$ 
\begin{tikzcd}
    A_{\tau_2}: \arrow[d, shift right=2] & \Gamma(E) \arrow[r] & \Gamma(H) &                                                \\
    A_{\tau_1}: \arrow[u, shift right]   & \Gamma(E) \arrow[r] & \Gamma(H) & {} \arrow[loop, distance=2em, in=305, out=235]
\end{tikzcd}
